---
title: "MyFirstLeaflet"
author: "Julio Cesar Marques"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Meu primeiro Mapa

```{r echo=FALSE}
library(leaflet)
my_map <- leaflet() %>% addTiles()
my_map
```

## Especificando local e colocando marcadores

```{r , echo=FALSE}
library(leaflet)
my_map <- my_map %>% addMarkers(lat=39.2980803, lng = -76.5898801,popup = "Jeff Leek's Offifce")

my_map <- leaflet() %>% addTiles() %>% addMarkers(lat=39.2980803, lng = -76.5898801,popup = "Jeff Leek's Offifce")

# my_map = addMarkers(lat=39.2980803, lng = -76.5898801,popup = "Jeff Leek's Offifce")
my_map
```

## Adicionando multiplos marcadores

```{r , eval=FALSE}
set.seed(2016-04-25)
df <- data.frame(lat = runif(20, min = 39.2, max = 39.3),
                 lng = runif(20, min = -76.6, max = -76.5))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers()

```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

